---
title: "Results"
---

<br>
<br>


## All convergence scores per package:algorithm sored by minimum RMSE

```{r echo=FALSE, message=FALSE, warning=FALSE}
if(file.exists("./data/TableAppendixC.csv")) {  
  Table1SupplApp <- read.csv("./data/TableAppendixC.csv", sep = ";") 
}else 
  Table1SupplApp <- rep("missing",8)

colnames(Table1SupplApp) <- c("Num", "Input format", "Maxit", "Learn.rate", "median",
                    "D51", "MAE", "WAE")

Table1SupplApp[, "Package"] <- Table1[Table1SupplApp$Num, "Package"]
Table1SupplApp[, "Algorithm"] <- Table1[Table1SupplApp$Num, "Algorithm"]
Table1SupplApp <- Table1SupplApp[, c("Package","Algorithm", "Input format", "Maxit", "Learn.rate", "median",
                    "D51", "MAE", "WAE")]


if(all(Table1SupplApp[, "Algorithm"] == Table1$Algorithm))
{
  Table1SupplApp <- Table1SupplApp[idxRk, ]
  rownames(Table1SupplApp) <- 1:NROW(Table1SupplApp)
}

Table1SupplApp <- Table1SupplApp %>%
  mutate(Learn.rate = as.character(Learn.rate)) %>%
  mutate(Learn.rate = ifelse(Learn.rate == "-", "N/A", Learn.rate))


kableExtra::kable(Table1SupplApp, align="llccccccc") %>%
  add_header_above(c(" "=2, "Input parameter"=3, "RMSE Score"=2, "Other score"=2)) %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

<br>
<br>


```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyr)

formatTable <- function(df) {
  colnames(df) <- c("Package::algorithm", "Time mean", "RMSE min", "RMSE median", "RMSE D51", 
                      "MAE median", "WAE median", "NPFA")
  
  df <- separate(data = df, col = "Package::algorithm", into = c("Package", "Algorithm"), sep = "::")
  return (df)
}
```


## Packages Tested per Multivariate Dataset {.tabset .tabset-fade .tabset-pills}

### mDette
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/mDette-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


### mFriedman
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/mFriedman-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



### mIshigami
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/mIshigami-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


### mRef153
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/mRef153-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

<br>

## Packages Tested per Univariate Dataset {.tabset .tabset-fade .tabset-pills}

### uDmod1
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uDmod1-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


### uDmod2
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uDmod2-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

### uDreyfus1
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uDreyfus1-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


### uDreyfus2
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uDreyfus2-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

### uGauss1
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uGauss1-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


### uGauss2
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uGauss2-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


### uGauss3
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uGauss3-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

### uNeuroOne
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uNeuroOne-result-summary.csv")) %>%
  kable(align="llccccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

<br>
<br>

# Summary statistics for top-10 packages on bWoodN1 Dataset

The table provides the summary statistics of top-10 NN packages over 20 runs on the large dataset `bWoodN1` which contains 20,000 rows with 6 inputs valued in [0,1] for a (single) numeric output.

```{r echo=FALSE, message=FALSE, warning=FALSE}

bwood_df <- read.csv("data/top-10-bwood.csv") %>% arrange(RMSE.median)
colnames(bwood_df) <- c("Package", "Time (mean)", "RMSE (min)", "RMSE (median)", "RMSE (D51)", "MAE (median)", "WAE (median)")
# bwood_df <- separate(data = bwood_df, col = "Package::algorithm", into = c("Package", "Algorithm"), sep = "::")
bwood_df %>%
  kable(align="lcccccc") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



