---
title: "Results"
---

<br>

This page contains results for all packages tested per dataset. The results are divided into two sections - Multivariate Datasets and Univariate Datasets. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyr)

formatTable <- function(df) {
  colnames(df) <- c("Package::algorithm", "Time mean", "RMSE min", "RMSE median", "RMSE D51", 
                      "MAE median", "WAE median", "NPFA")
  
  df <- separate(data = df, col = "Package::algorithm", into = c("Package", "Algorithm"), sep = "::")
  return (df)
}
```

<br>
<br>

# Multivariate Datasets {.tabset .tabset-fade .tabset-pills}

## mDette
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/mDette-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


## mFriedman
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/mFriedman-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



## mIshigami
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/mIshigami-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


## mRef153
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/mRef153-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

<br/>
<br/>

# Univariate Datasets {.tabset .tabset-fade .tabset-pills}

## uDmod1
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uDmod1-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


## uDmod2
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uDmod2-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## uDreyfus1
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uDreyfus1-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


## uDreyfus2
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uDreyfus2-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## uGauss1
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uGauss1-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


## uGauss2
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uGauss2-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


## uGauss3
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uGauss3-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## uNeuroOne
```{r echo=FALSE, message=FALSE, warning=FALSE}

formatTable(read.csv("data/tables-extra/uNeuroOne-result-summary.csv")) %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```


# Summary statistics for top-5 packages

The table provides the summary statistics of top-5 NN packages over 20 runs on the large dataset `bWoodN1` which contains 20,000 rows with 6 inputs valued in [0,1] for a (single) numeric output.

```{r echo=FALSE, message=FALSE, warning=FALSE}

bwood_df <- read.csv("data/Table3.csv")
colnames(bwood_df) <- c("Package::algorithm", "RMSE min", "RMSE median", "RMSE D51", "MAE median", "WAE median", "Time Median")
bwood_df <- separate(data = bwood_df, col = "Package::algorithm", into = c("Package", "Algorithm"), sep = "::")

bwood_df %>%
  kable(align="l") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```



